### 2017-12-12 README.Rmd
update readme

`drtmle` is an R package that computes marginal means of an outcome under fixed
levels of a treatment. The package computes targeted minimum loss-based (TMLE)
estimators that are doubly robust, not only with respect to consistency, but
also with respect to asymptotic normality, as discussed in Benkeser, Carone, van
der Laan \& Gilbert, 2017 (_accepted Biometrika_; [working
paper](http://biostats.bepress.com/ucbbiostat/paper356/)). This property
facilitates construction of doubly-robust confidence intervals and hypothesis
tests.

@@

Suppose the data consist of a vector of baseline covariates (`W`), a multi-level
treatment assignment (`A`), and a continuous or binary-valued outcome (`Y`). The
function `drtmle` may be used to estimate $E[E(Y \mid A = a_0, W)]$ for
user-selected values of $a_0$ (via option `a_0`). The resulting targeted minimum
loss-based estimates are doubly robust with respect to both consistency and
asymptotic normality. The function computes doubly robust covariance estimates
that can be used to construct doubly robust confidence intervals for marginal
means and contrasts between means. A simple example on simulated data is shown
below. We refer users to the vignette for more information and further examples.

```{r}
# load packages
library(drtmle, quietly = TRUE)
library(SuperLearner, quietly = TRUE)

@@

After using the `drtmle` R package, please cite the following:

        @article{benkeser2017improved,
          year  = {2017},
          author = {Benkeser, David C and Carone, Marco and van der Laan, Mark J
            and Gilbert, Peter B},
          title = {Doubly-robust nonparametric inference on the average
            treatment effect},
          journal = {Biometrika}
        }

>>>>

`drtmle` is an R package that computes marginal means of an outcome under fixed
levels of a treatment. The package computes targeted minimum loss-based (TMLE)
estimators that are doubly robust, not only with respect to consistency, but
also with respect to asymptotic normality, as discussed in [Benkeser, et al (2017)](https://doi.org/10.1093/biomet/asx053). This property
facilitates construction of doubly-robust confidence intervals and hypothesis
tests.

@@

Suppose the data consist of a vector of baseline covariates (`W`), a multi-level
treatment assignment (`A`), and a continuous or binary-valued outcome (`Y`). The
function `drtmle` may be used to estimate $E[E(Y \mid A = a_0, W)]$ for
user-selected values of $a_0$ (via option `a_0`). The resulting targeted minimum
loss-based estimates are doubly robust with respect to both consistency and
asymptotic normality. The function computes doubly robust covariance estimates
that can be used to construct doubly robust confidence intervals for marginal
means and contrasts between means. A simple example on simulated data is shown
below. We refer users to [the vignette](https://benkeser.github.io/drtmle/articles/using_drtmle.html) for more information and further examples.

```{r}
# load packages
library(drtmle)
library(SuperLearner)

@@

After using the `drtmle` R package, please cite the following:
  @Manual{drtmlepackage,
    title = {drtmle: Doubly-Robust Nonparametric Estimation and Inference},
    author = {David Benkeser},
    note = {R package version 1.0.0},
    doi = {10.5281/zenodo.844836},
  }
  @article{benkeser2017improved,
    year  = {2017},
    author = {Benkeser, David C and Carone, Marco and van der Laan, Mark J
      and Gilbert, Peter B},
    title = {Doubly-robust nonparametric inference on the average
      treatment effect},
    journal = {Biometrika},
    volume = {104}, number = {4},
    pages = {863–880},
    doi = {10.1093/biomet/asx053}
  }
